---
title: "Assignment 8 - Financial Time Series"
author: "Hailong Zeng, Qian Liu, Sifan Du, Zhengyi Qin"
date: "April 17, 2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
  - \newcommand\be{\begin{enumerate}}
  - \newcommand\ee{\end{enumerate}}
---

## Problem 1
Tsay's book. 7.1 (a), (b), (c). For (b) and (c), start with ARMA+GARCH model being an AR(2)+GARCH(1,1) then check if AR components are significant, and if GARCH(1,1) is adequate.\newline
Question7.1\newline
Consider the daily returns of GE stock from January 2, 1998, to December 31, 2008. The data can be obtained from CRSP or the file d-ge9808.txt. Convert the simple returns into log returns. Suppose that you hold a long position on the stock valued at $1 million. Use the tail probability 0.01. Compute the value at risk of your position for 1-day horizon and 15-day horizon using the following methods:

```{r, message=FALSE, warning=FALSE}
data = read.table("d-ge9808.txt",header=T)
ge = -log(data$ge+1) # log return
```

\be
\item[a] The RiskMetrics method.
```{r}
source("Igarch.R")
m1=Igarch(ge,include.mean=F,volcnt=F)
vt = 0.9604*(m1$volatility[2767])^2+(1-0.9604)*(ge[2767])^2
VaR1 = qnorm(1-0.01)*sqrt(vt)
paste('VaR for 1-day =', VaR1)
VaR15 = sqrt(15)*VaR1
paste('VaR for 15-day =', VaR15)
```

The value at risk of position for 1-day horizon in dollar amount is 1000000$\times$0.11577=115770. And the value at risk of position for 15-day horizon in dollar amount is 1000000$\times$0.4482=448200.







